---
title: "Topic 6: Topic Analysis"
author: "Felicia Cruz, Mia Forsline, Cullen Molitor, Marie Rivers"
date: '2022-05-10'
output: 
  pdf_document: default 
  html_document: default 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE, 
                      warning = FALSE)
```

```{r, include=FALSE}
# options(tinytex.verbose = TRUE)
```

```{r packages, message=FALSE, warning=FALSE}
#install packages if necessary, then load libraries
if (!require(librarian)){
  install.packages("librarian")
  library(librarian)
}

librarian::shelf(
  forcats, 
  ggplot2,
  ggraph,
  here,
  igraph, #network plots
  kableExtra,
  ldatuning,
  LDAvis,
  lubridate,
  palettetown,
  pdftools,
  quanteda,
  quanteda.textstats,
  quanteda.texplots,
  readr,
  readtext, #quanted subpackage for reading pdfs
  reshape2,
  stringr,
  tidyr,
  tidytext,
  tidyverse,
  tm,
  topicmodels,
  "tsne",
  widyr
  )
```

# Read in the data from PDF files in the "data" directory 

```{r}
#character of full file paths for each PDF in the data folder 
files <- list.files(path = here("data"),
                    pattern = "pdf$", full.names = TRUE)
#create a list
scripts <- lapply(files, pdf_text)

#create a readtext/dataframe of all PDF scripts 
scripts_pdf <- readtext(file = here("data", "*.pdf"),
                              docvarsfrom = c("metadata", "filenames", "filepaths"),
                              sep = "_")
```

# Create a clean corpus 
```{r}
#creating an initial corpus containing our data
script_corp <- corpus(x = scripts_pdf, text_field = "text" )

#check the corpus 
summary(script_corp) %>% 
  knitr::kable(caption = "Summary of Movie Script Corpus")
```

Add additional, context-specific stop words to stop word lexicon
```{r}
# more_stops <-c("2015",
#                "2016", 
#                "2017", 
#                "2018", 
#                "2019", 
#                "2020", 
#                "www.epa.gov", 
#                "https")
# add_stops <- tibble(word = c(stop_words$word, more_stops)) 
# stop_vec <- as_vector(add_stops)
```

Tokenize the data into single words and remove stop words 
```{r}
toks <- tokens(script_corp, 
               remove_punct = TRUE, 
               remove_numbers = TRUE)

# xxx...add custom stop words such as character names from "Don't Look Up"
add_stops <- c(stopwords("en"),"xxx", "yyy", "zzz")

toks1 <- tokens_select(toks, pattern = add_stops, selection = "remove")
```

# Convert to a document-feature matrix (dfm)
```{r}
dfm_comm <- dfm(toks1, tolower = TRUE)
dfm <- dfm_wordstem(dfm_comm)
dfm <- dfm_trim(dfm, 
                min_docfreq = 3, #keep terms that appear in at least 3 documents 
                min_termfreq = 1) #keep terms that appear at least once

dfm %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"),
                latex_options = "HOLD_position") #hold the table position when knitting
```
Remove rows (AKA documents) with all zeroes - otherwise the topic model won't work 
```{r}
sel_idx <- slam::row_sums(dfm) > 0 
dfm <- dfm[sel_idx, ]

dfm %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"),
                latex_options = "HOLD_position") #hold the table position when knitting
```

# Choose a number of latent topics (k) and run the Gibbs topic analysis 

```{r}
k <- 7 #k is the number of topics

topicModel_k7 <- LDA(dfm, 
                     k, 
                     method="Gibbs", 
                     control=list(iter = 500, verbose = 25))
```


```{r}
tmResult <- posterior(topicModel_k7)
#attributes(tmResult) #terms and topics 
 
beta <- tmResult$terms   # get beta from results
#dim(beta)                # K distributions over nTerms(DTM) terms 

terms(topicModel_k7, 10) #view the terms from each topic 
```

# Calculate metrics from the data 

## CaoJuan 2009 & Deveaud2014 method 

It seems like 7 topics is the ideal number 

```{r}
result <- FindTopicsNumber(
  dfm,
  topics = seq(from = 2, to = 20, by = 1),
  metrics = c("CaoJuan2009",  "Deveaud2014"),
  method = "Gibbs",
  control = list(seed = 77),
  verbose = TRUE
)

FindTopicsNumber_plot(result)
```
## Griffiths2004 & CaoJuan2009 method 

```{r}
result <- FindTopicsNumber(
  dfm,
  topics = seq(from = 2, to = 20, by = 1),
  metrics = c("CaoJuan2009", "Griffiths2004"),
  method = "Gibbs",
  control = list(seed = 77),
  verbose = TRUE
)

FindTopicsNumber_plot(result)
```
## Deveaud2014 method 

```{r}
result <- FindTopicsNumber(
  dfm,
  topics = seq(from = 2, to = 20, by = 1),
  metrics = c("CaoJuan2009", "Deveaud2014"),
  method = "Gibbs",
  control = list(seed = 77),
  verbose = TRUE
)

FindTopicsNumber_plot(result)
```


# Extract theta and beta values 

```{r}
theta <- tmResult$topics
beta <- tmResult$terms
vocab <- (colnames(beta))
```

Note that the beta value indicates how likely a term is to be in that particular topic 

```{r}
comment_topics <- tidy(topicModel_k7, matrix = "beta")

top_terms <- comment_topics %>%
  group_by(topic) %>%
  top_n(10, beta) %>%
  ungroup() %>%
  arrange(topic, -beta)

top_terms
```
# Graph the most likely words per topic 

```{r}
top_terms %>%
  mutate(term = reorder(term, beta)) %>%
  ggplot(aes(term, beta, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  coord_flip()
```

# Assign topic names based on the first 5 words 

```{r}
top5termsPerTopic <- terms(topicModel_k7, 5)
topicNames <- apply(top5termsPerTopic, 2, paste, collapse=" ")
```

# Explore the theta matrix 

The theta matrix contains the distribution of each topic over each document

```{r}
exampleIds <- c(1, 2, 3)
N <- length(exampleIds)

#lapply(epa_corp[exampleIds], as.character) #uncomment to view example text
# get topic proportions form example documents

topicProportionExamples <- theta[exampleIds,]

colnames(topicProportionExamples) <- topicNames

rownames(topicProportionExamples) <- c("Before the Flood", 
                                       "Don't Look Up", 
                                       "Inconvient Truth")

vizDataFrame <- melt(cbind(data.frame(topicProportionExamples),
                           document=factor(1:N)), 
                           variable.name = "topic", 
                           id.vars = "document")  %>% 
    mutate(document = case_when(
    document == 1 ~ "Before the Flood",
    document == 2 ~ "Don't Look Up",
    document == 3 ~ "Inconvient Truth"))
```

# Plot the distribution of each topic over each document 

```{r}
ggplot(data = vizDataFrame, aes(topic, value, fill = document)) +
  geom_bar(stat="identity") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +  
  coord_flip() +
  facet_wrap(~ document, ncol = N) + 
  labs(y = "Topic Distribution", 
       x = "Topic Name",
       fill = "Film") + 
  scale_fill_poke(pokemon = 137, spread = 3) + 
  theme_classic()
```

Here’s a neat JSON-based model visualizer

```{r}
#library(LDAvis)
#library("tsne")
svd_tsne <- function(x) tsne(svd(x)$u)

json <- createJSON(
  phi = tmResult$terms, 
  theta = tmResult$topics, 
  doc.length = rowSums(dfm), 
  vocab = colnames(dfm), 
  term.frequency = colSums(dfm),
  mds.method = svd_tsne,
  plot.opts = list(xlab="", ylab="")
)

serVis(json)
```

